Figures and results for main manuscript

### 2020-10-09 analysis/reports/manuscript_main.Rmd
remove render reports from namespace

>>>>

ggplot(all_di, aes(x = log_s0, y = log_n0, color = dat)) +
  geom_point(alpha = .01) +
  geom_point(data = filter(all_di, log_nparts > log(50)), alpha = .4) +
  theme_bw() +
  scale_color_viridis_d() +
  ggtitle("Communities by S and N") +
  facet_wrap(vars(dat), scales = "free") +
  geom_vline(xintercept = log(40)) +
  geom_hline(yintercept = log(1000))
